---
title: "CIHI Wait Time Sample Report"
author: "Emelie & Ben"
date: '`r format(Sys.time(), "%B %d, %Y")`'
header-includes:
- \usepackage{fancyhdr}
- \usepackage{ragged2e}
- \pagestyle{fancy}
- \fancyhead[CO,CE]{This is fancy header}
- \fancyfoot[CO,CE]{And this is a fancy footer}
- \fancyfoot[LE,RO]{\thepage}
---

```{r, echo = FALSE, warning = FALSE, message = FALSE}

# Load packages
library(readxl)
library(dplyr)
library(ggplot2)
library(directlabels)

library(sp)
library(ggmap)
library(maps)
library(maptools) # read shapefiles
library(rgdal) # read shapefiles
library(ggmap)
library(gpclib) # This has restrictive license, but maybe needed for foritfy if there is no rgeos
library(rgeos) # Suppose to be a free alternative for gpclib
library(raster) 

# Import data
waitTime_prov_df <- read_excel("www/CIHI treatment wait time.xlsx", "To R Prov")
# Add a dummy indicator
waitTime_prov_df$MetB <- ifelse(waitTime_prov_df$MetBenchmark > 90, "Met", "Not Met")
# reorder from west to east using factor
waitTime_prov_df$Prov <- factor(waitTime_prov_df$Province, 
                       levels = c("B.C.", "Alta.", "Sask.", "Man.", "Ont.", "Que.", "N.B.", "P.E.I.",
                                  "N.S.", "N.L.", "Canada"))

# Create subset
subdata_trt_x_prov_df <- filter(waitTime_prov_df, Treatment == input$ui_trt, Province != "Canada")
subdata_prov_df <- filter(waitTime_prov_df, Province == input$ui_prov)
wait_50 <- filter(waitTime_prov_df, Province == input$ui_prov, Treatment == input$ui_trt, Year == 2014)$Percentile50


# Read in the shape file
map_canada <- readShapeSpatial("www/prov4map/prov4map.shp")
# use Prov_Code as the region ID
mapo <- fortify(map_canada, region="Prov_Code")
```

![alt text](`r paste0('www/',gsub("\\.","",input$ui_prov),'_flag.png')`)

## CIHI Wait Time for `r input$ui_trt` in `r input$ui_prov`

This is a sample report based on the [Canadian Institute of Health Information (CIHI)](https://www.cihi.ca/en) wait time data.

We can customize anything you see on the page or on screen, from numbers to formatting, to suit your reporting needs and branding requirements.

Reports are created on the fly based on the province you selected on the dashboard. Right now, you are reading a provincial report on treatment wait time for `r input$ui_prov`, which shows the 50th Percentile wait time for `r input$ui_trt` in 2014 is `r wait_50` days.

The same report template creates the document you are reading now, which could be a PDF, Word document, or html page (or an interactive presentation slide!). This affords great flexibility as each format has its strengths and weaknesses.

* PDF report is great when you require precise control of your document layout and fomratting
* HTML report is perfect when you want to add interactive graphs and elements
* Word report is best when you want to further fine-tune the style and format of your report

With Neater Report, you are in control. You choose which format you want, all with the click of a button :)

## Data Source 

The wait time data is compiled annually by [CIHI](http://waittimes.cihi.ca).

\newpage


## Treatment

**Table** can be added and their stylings can be customized.

Table 1 shows trends of treatment wait time over time for each of the 10 provinces in Canada.

```{r, echo=FALSE, results='asis'}
kable(head(subdata_trt_x_prov_df[c(1,3,5:8)], 10),
      digits = 1,
      caption = paste0("Table 1 - Volume, Benchmark, 50th and 90th Percentile Wait Time of Treatments for ", input$ui_prov, " from 2008 to 2014"),
      row.names = FALSE,
      align = c("l",rep("c",6))
      )
```

\newpage

**Graph** can be added and positioned anywhere in the report, from a simple bar graph to advanced statistical graphics. Graph can be common to all reports, like this national comparison graph (see Figure 1).

**Figure 1 50th Percentile Wait Time for `r input$ui_trt` by Province between 2008 and 2014**

```{r, echo=FALSE, warning = FALSE, message=FALSE}
 
plot_data <- subdata_trt_x_prov_df
    
p <- ggplot(plot_data, aes(factor(Year), Percentile50, group=Province, size = Volume)) +
      geom_line(aes(colour = "Province")) + 
      geom_line(aes(colour = Region)) + # double plotting trick to get the direct label right
      theme_bw() + 
      scale_colour_manual(values=c("grey80","#a6cee3","grey80","#1f78b4", rep("grey80",9),"#b2df8a","black")) + scale_size_continuous(range = c(.3, 5)) + # need to manually set the colour for direct label
      xlab("") + ylab("50th Percentile (Day)") + 
      theme(axis.text = element_text(colour = "#1F77B4", size = rel(.7)),
            axis.title = element_text(colour = "#2CA02C", size = rel(.7)),
            panel.grid.major = element_line(colour = "grey70", size = .2, linetype = "dotted"),
            panel.border = element_blank(),
            legend.key = element_blank(),
            legend.text = element_text(colour = "grey60"),
            legend.title = element_text(colour = "#2CA02C"))
    
    direct.label(p, list('last.qp', cex=.7))
```

\newpage

A graph can also be specific to a subreport, such as the `r input$prov` graph shown in Figure 2.

**Figure 2 Wait Time of Various Treatment over Time for `r input$ui_prov` **

```{r echo=FALSE,  warning = FALSE, message=FALSE, fig.height = 6}
   
plot_data <- subdata_prov_df
    
  # need to use complete case or else facet has problem with missing
   # The 90th percentile seem to work fine as a proxy
   # Might lose some data but
   plot_data <- plot_data[complete.cases(plot_data$Percentile90),]
   
   # to add legend for separate geom line or area without melting or gather
   # melt won't work because ribbon doens't accept graident in ggplot2 or so they say
   # see http://stackoverflow.com/questions/10349206/add-legend-to-ggplot2-line-plot
   
   ggplot(plot_data, aes(factor(Year), Percentile90, group=factor(Treatment))) + 
     geom_area(aes(factor(Year), Percentile90, group=factor(Treatment), 
                   fill = "90th Percentile"), size = 1.3) + 
     geom_line(aes(factor(Year), Percentile90, group=factor(Treatment),
                   colour = MetB), size = 1.3) +
     geom_area(aes(factor(Year), Percentile50, group=factor(Treatment), 
                   fill = "50th Percentile"), size = 1.3) + 
     facet_wrap(~Treatment, ncol = 2) + 
     theme_fivethirtyeight() + 
     scale_fill_manual("", 
                       breaks = c("90th Percentile", "50th Percentile"),
                       values = c("#fee8c8","#fdbb84")) +
     theme(legend.position = "top",
           axis.text = element_text(size = rel(.7)),
           axis.title = element_text(size = rel(.7)),
           strip.text = element_text(size = rel(.7)),
           legend.text = element_text(size = rel(.7)),
           legend.title = element_text(size = rel(.7))) + ylab("") +
     guides(colour=guide_legend(title = "Met Benchmark?"),
          fill=guide_legend(title = "Percentile (Days)", nrow=1,byrow=TRUE))
     
```

\newpage

**Map** such as this choropleth map can be incoporated in a report.

```{r echo=FALSE, warning = FALSE, message=FALSE, fig.height = 6}
   
   plot_data <- subdata_trt_x_prov_df
   
 # assign id for merging with shapefile
    plot_data$id <- as.character(plot_data$Prov_Code)
    
    # Join the data
    mapo2 <- left_join(mapo, plot_data)
    
    # Map it!
    ggplot() + geom_polygon(data = filter(mapo2, !is.na(Year)), aes(long, lat, group = group, fill = MetBenchmark/100), color = NA) + facet_wrap(~Year, ncol = 2) + theme_nothing(legend = TRUE) + 
      scale_fill_distiller(palette = "PuRd", labels = percent,
                           breaks = pretty_breaks(n = 5), values = c(1,0)) +
      labs(title = "% Met Brenchmark",
           fill = "") +  guides(fill = guide_legend(reverse = TRUE)) +
      theme(strip.background = element_rect(fill = "white"),
            strip.text = element_text(size = rel(1.2), colour = "grey70"),
            plot.margin = unit(c(1,1,1,1),"cm"),
            plot.title=element_text(size = 18, vjust=3, colour = "#2CA02C"))
   
```
