---
title: "HPHS Beta App"
date: June 26, 2016
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
    theme: flatly
    css: styles.css
runtime: shiny
---


```{r setup, include = FALSE}

# Author: Benedito Chou & Emelie Gustafsson

```

```{r check, include = FALSE}

# Check
output$check <- renderPrint({
  unique(prepre_df()$Organization)
})

```


Quadrant {data-navmenu="Transition to Value"}
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------

```{r input_quadrant_txt}

fillCol(height = 600, flex = c(NA, 1), # NA sets natural height for inputs
        
  inputPanel(
    
    selectizeInput("year_txt", label = "Year", 
                   choices = c(2015, 2016), 
                   selected = 2016),
    
    selectizeInput("organization_txt", label = "Organization",
                   choices = c("Select One"))
  )

)

```


```{r comp_quadrant}

# Keep only overall
quadrant_pre_df <- reactive({
  df <- filter(core_survey_df, EvaluatorRole == "Overall", Year == input$year_txt)
})

# Update filters
observeEvent(input$year_txt, {
  org <- unique(quadrant_pre_df()$Organization)
  updateSelectizeInput(session, "organization_txt", choices = org)
})

# Assign quadrant at the rollup competency level
quadrant_txt_df <- reactive({
   
  df <- filter(quadrant_pre_df(), Organization == input$organization_txt)

  # Calculate overall mean and SD
  df <- mutate(df, overAllM_proficiency = mean(ProficiencyM, na.rm = T), 
             overAllM_priority = mean(PriorityM, na.rm = T))
  
  # Summarize and assign by competency
  df_group <- group_by(df, Competency) %>%
    dplyr::summarize(ProficiencyM = mean(ProficiencyM, na.rm = T),
            PriorityM = mean(PriorityM, na.rm = T),
            overAllM_proficiency = mean(overAllM_proficiency),
            overAllM_priority = mean(overAllM_priority)) %>%
    dplyr::mutate(quadrant = ifelse(ProficiencyM <= overAllM_proficiency & PriorityM > overAllM_priority, "RFI", ""),
         quadrant = ifelse(ProficiencyM > overAllM_proficiency & PriorityM > overAllM_priority, "FCI", quadrant),
         quadrant = ifelse(ProficiencyM > overAllM_proficiency & PriorityM <= overAllM_priority, "CIRR", quadrant),
         quadrant = ifelse(ProficiencyM <= overAllM_proficiency & PriorityM <= overAllM_priority, "CVAM", quadrant))
  
  })

```

Column
-----------------------------------------------------------------------

### Ready for Improvment (RFI) <br> (Motivated to act, limited ability)

```{r RFI}

renderUI({

RFI_list <- filter(quadrant_txt_df(), quadrant == "RFI") %>% select(Competency)

RFI_head <- NULL
for (i in RFI_list) {
  RFI_head <- paste0("<h4>",i,"</h4>")
}

HTML(RFI_head)

})


```

### Communicate Vistion, Align & Motivate (CVAM) (Not motivated or able)

```{r CVAM}

renderUI({
  
CVAM_list <- filter(quadrant_txt_df(), quadrant == "CVAM") %>% select(Competency)

CVAM_head <- NULL
for (i in CVAM_list) {
  CVAM_head <- paste0("<h4>",i,"</h4>")
}

HTML(CVAM_head)

})

```

Column
-----------------------------------------------------------------------

### Focus on Continuous Improvement (FCI) (Motivated and able)

```{r FCI}

renderUI({
  
FCI_list <- filter(quadrant_txt_df(), quadrant == "FCI") %>% select(Competency)

FCI_head <- NULL
for (i in FCI_list) {
  FCI_head <- paste0("<h4>",i,"</h4>")
}

HTML(FCI_head)

})

```

### Clarify Importance or Redirect Resources (CIRR) (Capable but not a high priority)

```{r CIRR}

renderUI({
  
CIRR_list <- filter(quadrant_txt_df(), quadrant == "CIRR") %>% select(Competency)

CIRR_head <- NULL
for (i in CIRR_list) {
  CIRR_head <- paste0("<h4>",i,"</h4>")
}

HTML(CIRR_head)

})

```


Table {data-navmenu="Transition to Value"}
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------

```{r input_quadrant_tbl}

fillCol(height = 600, flex = c(NA, 1), # NA sets natural height for inputs
        
  inputPanel(
    
    selectizeInput("year_tbl", label = "Year", 
                   choices = c(2015, 2016), 
                   selected = 2016),
    
    selectizeInput("organization_tbl", label = "Organization",
                   choices = c("Select One"))
  )

)

```

Column
-----------------------------------------------------------------------

### Transition to Value Table {.no-title}

``` {r quadrant_table}

# Keep only overall
quadrant_tbl_pre_df <- reactive({
    df <- filter(core_survey_df, EvaluatorRole == "Overall", Year == input$year_tbl)
})

# Update filters
observeEvent(input$year_tbl, {
  org <- unique(quadrant_tbl_pre_df()$Organization)
  updateSelectizeInput(session, "organization_tbl", choices = org)
})

# Make quadrant table
renderDataTable({
  
  df <- filter(quadrant_tbl_pre_df(), Organization == input$organization_tbl)
  
  # Convert variable to factor for easy table filter
  df$group <- factor(df$group, level = c("RFI","FCI","CIRR","CVAM"))
  df$Competency <- factor(df$Competency)
  
  # Round numbers for easy table filter
  df$Alignment <- round(df$Alignment, 2)
  df$ProficiencyM <- round(df$ProficiencyM, 2)
  df$PriorityM <- round(df$PriorityM, 2)
  
  df <- df %>%
    select(group, Statement, Competency, `Priority Rank`, Alignment, ProficiencyM, PriorityM) %>% arrange(group) %>%
    rename(Quadrant = group,
           Driver = Statement,
           `Alignment Score` = Alignment,
           `Avg Proficiency` =  ProficiencyM,
           `Avg Priority` = PriorityM)
    
  datatable(df,
            rownames = FALSE,
            filter = list(position = "top", clear = TRUE)) %>%
    formatRound(c('Alignment Score', 'Avg Proficiency', 'Avg Priority'), 2)
  
})


```


Transition to Value Quadrant
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------

```{r input_quadrant}

fillCol(height = 600, flex = c(NA, 1), # NA sets natural height for inputs
        
  inputPanel(
    
    selectizeInput("domain", label = "Domain",
                   choices = c("All",
                               "Management Structure",
                               "Performance Management",
                               "Patient Engagement",
                               "Care Delivery"),
                   selected = "All",
                   multiple = TRUE),
    
    selectizeInput("competency_quad", label = "Competency",
                   choices = c("All",
                               "Clarity of Mission (CM)",
                               "Balanced Governance Structure (BGS)",
                               "Provider Education (PED)",
                               "Provider Engagement (PEN)",
                               "Identification of Patient Health Needs (IPHN)",
                               "Clinical Quality and Health Outcomes Measurement (CQHM)",
                               "Practice Pattern Analysis (PPA)",
                               "Budgeting and Capital Planning (BCP)",
                               "Contracting (C)",
                               "Compensation Alignment (CA)",
                               "Appropriate Mix of Providers and Care Settings (APCS)",
                               "Care Guidelines (CG)",
                               "Care Decision Support (CDS)",
                               "Patient Activation (PA)",
                               "Patient Self-Management (PSM)",
                               "Patient Education (PE)"),
                   selected = "All",
                   multiple = TRUE),
    
    selectizeInput("year", label = "Year", 
                   choices = c(2015, 2016), 
                   selected = 2016),
    
    selectizeInput("organization", label = "Organization",
                   choices = c("Select One"))
  )

)

```

Column
-----------------------------------------------------------------------

### Transition to Value Quandrant 

```{r data_filter, include=FALSE}

# An elegant multi-stage data filter design, inspired by JAEG!

# First tage filter
pre_df <- reactive({
  
  df <- filter(core_survey_df, Year == input$year,
               EvaluatorRole == "Overall")
  
  if (is.null(input$domain)) {
    df <- df
  } else if (input$domain != "All") {
    df <- filter(df, Domain %in% input$domain)
  }

  if (is.null(input$competency_quad)) {
    df <- df
  } else if (input$competency_quad != "All") {
    df <- filter(df, Competency %in% input$competency_quad)
  }
  
  return(df)
})


# Second Stage Filter
survey_df <- reactive({
  
  df <- pre_df()
  
  if (!is.null(input$organization) || input$organization != "Select One") {
    df <- filter(df, Organization == input$organization)
  }
  
})

# Update filters
observeEvent(input$year, {
  org <- unique(pre_df()$Organization)
  updateSelectizeInput(session, "organization", choices = org)
})

```

```{r graph_quadrant}

# Quadrant Plot
plotlyOutput("graph_quadrant", height = "100%")

output$graph_quadrant <- renderPlotly({
  
  df <- survey_df()
  
  key <- row.names(df)
  
  # d <- event_data("plotly_hover")
  
  req(survey_df()) 
  
  # if (!is.null(d$key)) {
  # df$EvaluatorRole <- ifelse(row.names(df) == d$key, "Yes", "No")
  # } else {
  # df <- df
  # }
  
  # Get overall proficiency and priority score for benchmark line
  overall_df <- filter(core_survey_df, Organization == "Overall")
  
  # Basic Scatterplot
  g <- ggplot(df, aes(x= ProficiencyM, y = PriorityM, fill = EvaluatorRole,
                      key = key,
                       text = paste("Question: ", QuestionCode,
                                    "<br>Competency: ", Competency,
                                    "<br>Proficiency: ", round(ProficiencyM, 1),
                                    "<br>Priority: ", round(PriorityM, 1),
                                    "<br>Rank: ", `Priority Rank`))) +
    geom_hline(aes(yintercept = mean(PriorityM, na.rm = T)), color = "orange", alpha = 1/2) + 
    geom_vline(aes(xintercept = mean(ProficiencyM, na.rm = T)), color = "orange", alpha = 1/2) + 
    geom_hline(data = overall_df, aes(yintercept = mean(PriorityM, na.rm = T)), color = "#a8ddb5", alpha = 2/3, linetype="dotted") + 
    geom_vline(data = overall_df, aes(xintercept = mean(ProficiencyM, na.rm = T)), color = "#a8ddb5", alpha = 2/3, linetype="dotted") + 
    geom_point(color = "darkgrey", alpha = 2/3, size = 3, shape = 21) + 
    theme_minimal() +
    ggtitle(unique(df$Organization)) +
    theme(legend.position = "none",
          axis.text = element_text(colour = "darkgrey"),
          axis.title = element_text(colour = "darkgrey"),
          panel.grid = element_line(colour = 'lightgrey', linetype = 'dotted')) +
    scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8,9), limits = c(1, 9)) +
    scale_y_continuous(breaks=c(1,2,3,4,5), limits = c(1, 5)) +
    scale_fill_manual(values=c("#8dd3c7","#ffffb3","#bebada", "#fb8072","#80b1d3", "#fdb462", "#b3de69", "#fccde5", "#d9d9d9", "#bc80bd")) +
    labs(x = "Average Proficiency",
         y = "Average Priority") # Doesnt seem to work with plolty
  
   # stat_ellipse(geom = "polygon", alpha = 1/10) + # too few points
  
   # plot_ly axis options
   ax <- list(
    zeroline = FALSE,
    showline = FALSE,
    showticklabels = TRUE,
    showgrid = TRUE,
    gridcolor = '#eee',
    gridwidth = 1
    )
  
  ggplotly(g, tooltip = "text") %>%
    layout(xaxis = ax, yaxis = ax)

})

# Plotly events listeners
output$hover <- renderPrint({
  d <- event_data("plotly_hover")
  if (is.null(d)) "Hover events appear here (unhover to clear)" else d
})

output$click <- renderPrint({
  d <- event_data("plotly_click")
  if (is.null(d)) "Click events appear here (double-click to clear)" else d
})

output$brush <- renderPrint({
  d <- event_data("plotly_selected")
  if (is.null(d)) "Click and drag events (i.e., select/lasso) appear here (double-click to clear)" else d
})

output$zoom <- renderPrint({
  d <- event_data("plotly_relayout")
  if (is.null(d)) "Relayout (i.e., zoom) events appear here" else d
})

```

Column
-----------------------------------------------------------------------

### Recommended Action Plan

```{r graph_priority}

renderPlotly({

  df <- survey_df()
  
  d <- event_data("plotly_hover")
  
  req(survey_df())  
  
  # key <- row.names(df)
  
  if (!is.null(d$key)) {
  df$highlight <- ifelse(row.names(df) == d$key, "Yes", "No")
  } else {
  df$highlight <- "No"
  }
  
  # Find out the max number of rank item
  maxrank <- group_by(df, group) %>%
    summarize(maxrank = max(`Priority Rank`, na.rm = T)) %>%
    ungroup() %>%
    summarize(max(maxrank, na.rm = T)) %>% as.numeric()
  
  # Create x-axis label
  axis_label <- 1:maxrank
  
  # Insert Priority Text
  axis_label[2] <- "2<br>Highest Priority"
  axis_label[maxrank - 1] <- paste0(max(maxrank) - 1,"<br>Lowest Priority")
  
  df$fakeheight <- 100
  
  g <- ggplot(df, aes(as.factor(`Priority Rank`), fakeheight, fill = highlight,
                        text = paste("Competency: ", Competency,
                                   "<br>Question: ", QuestionCode,
                                   "<br>Statement: ", Statement,
                                   "<br>Quadrant Rank: ", `Priority Rank`))) +
          geom_bar(stat = "identity", width = .6) + 
    facet_grid(group~.) +
    geom_text(aes(label = QuestionCode), size = .9, nudge_y = -5) +
    theme_minimal() +
    theme(legend.position="none",
          panel.grid = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.text = element_text(colour = "darkgrey"),
          axis.title.x = element_text(colour = "darkgrey")) +
    scale_x_discrete(breaks=seq_along(1:maxrank), labels = axis_label) +
    labs(x = "Recommended Priorities by Quadrant and Driver") +
    scale_fill_manual(values = c("#f7f7f7", "#a8ddb5"))

  ggplotly(g, tooltip = "text")

})

```


Response Distribution
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------

```{r input_bar}

inputPanel(
  
   selectizeInput("year_bar", label = "Year", 
                   choices = c(2015, 2016), 
                   selected = 2016),
   
    selectizeInput("org", label = "Organization",
                   choices = c("Select One")),
   
    selectizeInput("quadrant", label = "Transition to Value Quadrant",
                   choices = c("All",
                               "FCI",
                               "RFI",
                               "CIRR",
                               "CVAM"),
                   selected = "All"),
   
    selectizeInput("competency_bar", label = "Competency",
                   choices = c("All",
                               "Clarity of Mission (CM)",
                               "Balanced Governance Structure (BGS)",
                               "Provider Education (PED)",
                               "Provider Engagement (PEN)",
                               "Identification of Patient Health Needs (IPHN)",
                               "Clinical Quality and Health Outcomes Measurement (CQHM)",
                               "Practice Pattern Analysis (PPA)",
                               "Budgeting and Capital Planning (BCP)",
                               "Contracting (C)",
                               "Compensation Alignment (CA)",
                               "Appropriate Mix of Providers and Care Settings (APCS)",
                               "Care Guidelines (CG)",
                               "Care Decision Support (CDS)",
                               "Patient Activation (PA)",
                               "Patient Self-Management (PSM)",
                               "Patient Education (PE)"),
                   select = "All"),
   
    selectizeInput("driver", label = "Driver",
                   choices = c("All", "CM1","BGS1","BGS2","BGS3","BGS4","PED1","PED2","PED3","PEN1","PEN2", "CDS1", "CDS2", "CDS3", "IPHN1", "IPHN2", "CQHM1", "CQHM2", "PPA1", "PPA2", "BCP1", "BCP2", "BCP3", "C1", "C2", "CA1", "CA2", "CA3", "APCS1", "APCS2", "APCS3", "CG1", "CG2", "CG3", "CG4", "CG5", "CG6", "PA1", "PA2", "PSM1", "PSM2", "PE1", "PE2"),
                   selected = "All"),
   
    selectizeInput("question_type", label = "Question Type",
                   choices = c("Proficiency" = "Proficiency", 
                               "Priority" = "Priority_Q"),
                   selected = "Proficiency")
)

```


```{r master_data, include = FALSE}

# An elegant multi-stage data filter design, inspired by JAEG!

# Pre Pre filter
prepre_df <- reactive({
    df <- filter(master_survey_df, Year == input$year_bar)
})

# Pre Pre 2 filter
prepre2_df <- reactive({
  df <- isolate(prepre_df())
  if (!is.null(input$org) || input$org != "Select One") {
    df <- filter(df, Organization == input$org)
  }
})

# Quandrant Scoring
scored_df <- reactive({
  
  df <- prepre2_df()

  # Calculate overall mean and SD
  df <- mutate(df, overAllM_proficiency = mean(Proficiency, na.rm = T), 
             overAllSD_proficiency = sd(Proficiency, na.rm = T),
             overAllM_priority = mean(Priority_Q, na.rm = T),
             overAllSD_priority = sd(Priority_Q, na.rm = T))
  
  # Summarize by question
  df_group <- group_by(df, QuestionCode) %>%
  dplyr::summarize(ProficiencyM = mean(Proficiency, na.rm = T),
            PriorityM = mean(Priority_Q, na.rm = T),
            overAllM_proficiency = mean(overAllM_proficiency),
            overAllSD_proficiency = mean(overAllSD_proficiency),
            overAllM_priority = mean(overAllM_priority),
            overAllSD_priority = mean(overAllSD_priority)) %>%
  dplyr::mutate(quadrant = ifelse(ProficiencyM <= overAllM_proficiency & PriorityM > overAllM_priority, "RFI", ""),
         quadrant = ifelse(ProficiencyM > overAllM_proficiency & PriorityM > overAllM_priority, "FCI", quadrant),
         quadrant = ifelse(ProficiencyM > overAllM_proficiency & PriorityM <= overAllM_priority, "CIRR", quadrant),
         quadrant = ifelse(ProficiencyM <= overAllM_proficiency & PriorityM <= overAllM_priority, "CVAM", quadrant))
  
  # Join data back with main data
  df <- inner_join(df, df_group, by = "QuestionCode")
  
})


pre_master_df <- reactive({
  
  df <- scored_df()
  
  if (is.null(input$quadrant)) {
    df <- df
  } else if (input$quadrant != "All") {
    df <- filter(df, quadrant %in% input$quadrant)
  }

  if (input$competency_bar == "All") {
    df <- df
  } else if (input$competency_bar != "All") {
    df <- filter(df, Competency %in% input$competency_bar)
  }
  
})

master_df <- reactive({
  
  df <- pre_master_df()

  if (input$driver == "All") {
    df <- df
  } else if (input$driver != "All") {
    df <- filter(df, QuestionCode %in% input$driver)
  }
  
})

# Update filters
observeEvent(input$year_bar, {
  org <- sort(unique(prepre_df()$Organization))
  updateSelectizeInput(session, "org", choices = org)
})

observeEvent(input$quadrant, {
  competency <- unique(pre_master_df()$Competency)
  updateSelectizeInput(session, "competency_bar", choices = c("All", competency))
})

observeEvent(input$competency_bar, {
  driver <- unique(pre_master_df()$QuestionCode)
  updateSelectizeInput(session, "driver", choices = c("All", driver))
})

```

Column
-----------------------------------------------------------------------

### Response Distribution

```{r graph_resp}

plotlyOutput("graph_resp", height = "100%")

output$graph_resp <- renderPlotly({
  
  # Pre summarize it
  df <- group_by_(master_df(), input$question_type) %>%
  summarise(n = n()) %>%
  mutate(percent = n/sum(n),
         pos = percent + .002)
  
  if (input$question_type == "Proficiency") {
    df <- filter(df, complete.cases(Proficiency))
    g <- ggplot(df, aes(x = Proficiency, y = percent, fill = as.factor(Proficiency)))
  } else if (input$question_type == "Priority_Q") {
        df <- filter(df, complete.cases(Priority_Q))
    g <- ggplot(df, aes(x = Priority_Q, y = percent, fill = as.factor(Priority_Q)))
  }

  g <- g + geom_bar(data = df, stat = "identity",
           aes(text = paste0("Percent: ", scales::percent(percent), "%"))) +
  geom_text(aes(label = scales::percent(percent), y = pos), size = 3) +
  theme_minimal() +
  theme(axis.title = element_blank(),
        axis.text = element_text(colour = "darkgrey"),
        axis.title.x = element_text(colour = "darkgrey")) +
  scale_x_discrete(limits=1:9) +
  scale_y_continuous(labels = percent_format())
  # scale_fill_brewer(direction = 1, guide = FALSE)
  
 if (input$question_type == "Proficiency") {
    g <- g + scale_fill_manual(values = c("#e6550d", "#fd8d3c", "#fdbe85", "#feedde",
"#eff3ff", "#bdd7e7", "#6baed6","#3182bd","#08519c"), guide = FALSE)
  } else if (input$question_type == "Priority_Q") {
    g <- g + scale_fill_manual(values = c("#e6550d", "#fdbe85", 
"#eff3ff", "#6baed6","#08519c"), guide = FALSE)
  }
  
  ggplotly(g, tooltip = "text") %>%
    layout(xaxis = list(showgrid = FALSE))

})

```

Column
-----------------------------------------------------------------------

### Response by Role

```{r graph_resp_by_role}

plotlyOutput("graph_resp_by_role", height = "100%")

output$graph_resp_by_role <- renderPlotly({
  
  if (input$question_type == "Proficiency") {
    df <- filter(master_df(), complete.cases(Proficiency)) %>% select(Proficiency, EvaluatorRole)
  } else if (input$question_type == "Priority_Q") {
    df <- filter(master_df(), complete.cases(Priority_Q)) %>% select(Priority_Q, EvaluatorRole)
  }
  
  # see http://stackoverflow.com/questions/34903368/how-to-center-stacked-percent-barchart-labels-in-ggplot2

  df <- group_by_(df, "EvaluatorRole", input$question_type) %>%
  summarise(n = n()) %>%
  mutate(percent = n/sum(n),
         pos = cumsum(percent) - 0.5 * percent)
  
  names(df)[2] <- "question_type"

 g <- ggplot(df, aes(x = EvaluatorRole, y = percent, fill = as.factor(question_type),
             text = paste0("Percent: ", round(percent * 100), "%"))) +
  geom_bar(stat="identity", width = .9, position = "fill") +
  geom_text(aes(label=ifelse(percent >= 0.07, paste0(sprintf("%.0f", percent*100),"%"),""),
                y=pos), colour="white") +
  coord_flip() +
  theme_minimal() +
  theme(axis.title = element_blank(),
        axis.text = element_text(colour = "darkgrey"),
        axis.title.x = element_text(colour = "darkgrey")) +
  scale_y_continuous(labels = percent_format())
  # scale_fill_brewer(direction = 1, guide = FALSE)
  
 if (input$question_type == "Proficiency") {
    g <- g + scale_fill_manual(values = c("#e6550d", "#fd8d3c", "#fdbe85", "#feedde",
"#eff3ff", "#bdd7e7", "#6baed6","#3182bd","#08519c"), guide = FALSE)
  } else if (input$question_type == "Priority_Q") {
    g <- g + scale_fill_manual(values = c("#e6550d", "#fdbe85", 
"#eff3ff", "#6baed6","#08519c"), guide = FALSE)
  }
 
  ggplotly(g, tooltip = "text") %>%
    layout(yaxis = list(showgrid = FALSE))

})


```


Comments
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------

```{r input_comment}

inputPanel(
  
   selectizeInput("year_comment", label = "Year", 
                   choices =  2016, 
                   selected = 2016),
   
    selectizeInput("org_comment", label = "Organization",
                   choices = unique(as.character(master_comment_2016$Organization)))
)

```

Column
-----------------------------------------------------------------------

### Comment

```{r comment_table}

renderDataTable({
  
  df <- dplyr::filter(master_comment_2016, Organization == input$org_comment)
  
  # Find matching cases via ID
  ID <- select(df, ResponseID)

  # Create aggregate summary set per ID
  df_score <- inner_join(ID, master_survey_df, by = c("ResponseID" = "EvaluatorID"))
  
  df_score <- group_by(df_score, ResponseID) %>%
                summarize(
                        `Avg Proficiency` = round(mean(Proficiency, na.rm = T), 2),
                        `Avg Priority` = round(mean(Priority_Q, na.rm = T), 2)
                        ) %>% ungroup()
  
  # Join proficiency and priority score data with comment for table
  df_m <- inner_join(df, df_score, by = "ResponseID")
  
  df_long <- tidyr::gather(df_m, Section, Comment, CMTXT:FTRPRIOTXT) %>% 
    filter(Comment != "") %>% 
    select(`Avg Proficiency`, `Avg Priority`, Section, Comment, Role) %>% 
    arrange(Section)
  
  df_long <- inner_join(df_long, text_label, by = c("Section" = "Code")) %>%
    select(-Section) %>%
    rename(Section = Label) %>%
    select(`Avg Proficiency`, `Avg Priority`, Comment, Role, Section)
  
  # Convert variable to factor for easy table filter
  df_long$Role <- factor(df_long$Role)
  df_long$Section <- factor(df_long$Section)

  datatable(df_long,
            rownames = FALSE,
            filter = list(position = "top", clear = TRUE)) %>%
     formatRound(c('Avg Proficiency', 'Avg Priority'), digits = 2)
  
})


```

Model {data-navmenu="Background Materials"}
=======================================================================

```{r ontology}

# Combine fillCol with iframe width and height set to 100%
# This create an empty div that expand and contract to fill all avaliable space
# Another JAEG-inspired solution!

fillCol(
  HTML('<iframe width="90%" height="92%" src="https://www.mindmeister.com/maps/public_map_shell/369317926/capabilities-assessment-ontology?width=600&height=400&z=auto&t=GCeTiIjrsf&presentation=1">'),
  HTML('
  <iframe style="border: 1px solid #777;" width="90%" height="92%" frameborder="0" src="https://www.mindmeister.com/maps/public_map_shell/369317926/capabilities-assessment-ontology?width=600&height=400&z=auto&t=GCeTiIjrsf&presentation=1" scrolling="no" style="overflow: hidden; margin-bottom: 5px;">Your browser is not able to display frames. Please visit <a href="https://www.mindmeister.com/369317926/capabilities-assessment-ontology?t=GCeTiIjrsf" target="_blank">Capabilities Assessment Ontology</a> on MindMeister.</iframe>
')
)

  # <div style="margin-bottom: 5px"><a href="https://www.mindmeister.com/369317926/capabilities-assessment-ontology?t=GCeTiIjrsf" target="_blank">Capabilities Assessment Ontology</a> by <a href="https://www.mindmeister.com/users/channel/5907489" target="_blank">Greg K</a></div>


```


Interactive PDF {data-navmenu="Background Materials"}
=======================================================================

```{r interactive_pdf}

fillCol(
  HTML('
  <iframe style="border: 1px solid #777;" src="https://indd.adobe.com/embed/0484dc8b-b36d-438d-9e16-5e0792a0ded0?startpage=1&allowFullscreen=true" width="90%" height="92%" frameborder="0" allowfullscreen=""></iframe>
  ')
)

```